Ecostructure Global Geographic Motifs, v2

### 2019-10-04 reports/ecostructure_geo/ecostructure_geo.Rmd
Output k=3 for the combined plot

```{r combined-plot}
make_geo_theta_plot_color <- function (geo_theta_long, border_color) {
  ggplot(ggplot2::map_data("world"), aes(x = long, y = lat)) +
  geom_polygon(aes(group = group), fill = "light grey") +
  geom_raster(data = geo_theta_long, aes(fill = theta)) +
  scale_fill_gradient(low = "darkseagreen3", high = "red") +
  coord_sf(ylim = c(-50, 90), datum = NA) +
  jntools::blank_x_theme() +
  jntools::blank_y_theme() +
  theme_void() +
  theme(
    legend.position = "none",
    plot.background = element_rect(fill = "transparent"),
    panel.background = element_rect(fill = "transparent"),
    panel.border = element_rect(colour = border_color, fill=NA, size=2)
  )
}

k_select <- 4

cols <- RColorBrewer::brewer.pal(k_select, name = "Set1")

ecos_plot_pie2(
    omega = results_list[[k_select - 1]][["omega"]],
    image_width = 6000*tweak,
    image_height = 4800*tweak,
    radius = 0.05,
    color = cols,
    bgmap_path = japan,
    long_lim = c(pull(all_cells, longitude) %>% min %>% floor, 
                 pull(all_cells, longitude) %>% max %>% ceiling),
    lat_lim =  c(pull(all_cells, latitude) %>% min %>% floor, 
                 pull(all_cells, latitude) %>% max %>% ceiling),
    path = glue::glue(here("reports/ecostructure_geo/geo_omega_combined_k={k_select}.png"))
  )

>>>>

```{r combined-plot}
# For easy tweaking of plot size to get pie charts
# to not overlap.
tweak <- 1.5

make_geo_theta_plot_color <- function (geo_theta_long, border_color) {
  ggplot(ggplot2::map_data("world"), aes(x = long, y = lat)) +
  geom_polygon(aes(group = group), fill = "light grey") +
  geom_raster(data = geo_theta_long, aes(fill = theta)) +
  scale_fill_gradient(low = "darkseagreen3", high = "red") +
  coord_sf(ylim = c(-50, 90), datum = NA) +
  jntools::blank_x_theme() +
  jntools::blank_y_theme() +
  theme_void() +
  theme(
    legend.position = "none",
    plot.background = element_rect(fill = "transparent"),
    panel.background = element_rect(fill = "transparent"),
    panel.border = element_rect(colour = border_color, fill=NA, size=2)
  )
}

k_select <- 3

cols <- RColorBrewer::brewer.pal(k_select, name = "Dark2")

ecos_plot_pie2(
    omega = results_list[[k_select - 1]][["omega"]],
    image_width = 6000*tweak,
    image_height = 4800*tweak,
    radius = 0.04,
    color = cols,
    bgmap_path = japan,
    long_lim = c(pull(all_cells, longitude) %>% min %>% floor, 
                 pull(all_cells, longitude) %>% max %>% ceiling),
    lat_lim =  c(pull(all_cells, latitude) %>% min %>% floor, 
                 pull(all_cells, latitude) %>% max %>% ceiling),
    path = glue::glue(here("reports/ecostructure_geo/geo_omega_combined_k={k_select}.png"))
  )
